title

### 2013-02-04 paper.tex
Changes

However, this isn't as simple as it may seem — it isn't enough to connect only a small number of cities with pipelines, because it's possible that droughts could occur in areas of the country not connected by those pipelines.
On the other hand, the cost of building pipelines in too many locations would be prohibitive.
Our paper solves this problem by finding a way to connect all of mainland USA with the minimum possible length of pipeline.
This solution is still quite expensive, at a projected cost of \$92 billion dollars, but given the massive cost to the economy of droughts such as the 2012-2013 drought, we contend that it will is the most cost-effective solution to the United States' water problems.

@@

We begin our paper with a projection of the likely levels of water
demand in the United States by 2025 on a county-by-county basis. Our primary source of data is the County-level water use data made publically available
by the US Geological Survey (USGS) in years 1985, 1990, 1995, 2000,
and 2005 \cite{key-2,key-3,key-4,key-5,key-6}. Using our projected
figures, we describe a means of minimizing the expected cost of constructing
water storage and water purification systems using a network flows
algorithm.

First, we project the County-level water needs in 2025 using water
use data from the years listed, making the assumption that water use
equals the current water demands.

@@

This paper is primarily concerned with the construction of new water
supply infrastructure. Thus, there are some aspects of the water management
process that will not be further considered: 
\begin{itemize}
\item Public education: As with all issues of resource conservation, the
behaviour of the general public has an effect on water supplies. This
will not be considered here, for several reasons. The key issue is
that there is a lack of empirical evidence suggesting that currently
known public education strategies will work to minimise water usage
in the United States (developing such strategies further is beyond
the scope of this paper). The United States in particular has been
particularly resistant to attempts to reduce per capita water consumption\cite{key-7}.
More generally, even water education programmes considered particularly
successful, such as that of Singapore, have not managed to make a
huge impact on consumption, with an approximate 5 per cent reduction
in household water use over 6 years\cite{key-8}. Finally, the effect
of water education programmes is likely to have a similar effect in
each location. This means that areas that would be most in need of
additional infrastructure taking into account such programmes would
be essentially the same as those areas most in need while not taking
into account such programmes. 
\item Maintenance costs of current infrastructure: minimizing maintenance
costs depends on technological advancement and management, but is
essentially a fixed cost irrespective of the new infrastructure we
decide to implement.
\item Cost of obtaining data: Much of our analysis depends on USGS data.
We note that the cost of obtaining this survey data is negligible
(the WaterSMART initiative, which collects much of the data, cost
\$21 million this year\cite{key-9}. In comparison, de-salinization
facilities can easily cost billions to construct\cite{key-10}) compared
to the utility of superior decision making in constructing water-related
infrastructure (among various other things the data is useful for).
\end{itemize}

@@

Based on the average cost of de-salinization facilities noted above, it would cost \$79 billion to build enough de-salinization plants to meet this demand:

>>>>

However, this isn't as simple as it may seem — it isn't enough to connect only a small number of cities with pipelines, because it's possible that droughts could occur in areas of the country not connected by those pipelines.
On the other hand, the cost of building pipelines in too many locations would be prohibitive.
Our paper solves this problem by finding a way to connect all of mainland USA with the minimum possible length of pipeline.
This solution is still quite expensive, at a projected cost of \$79 billion dollars for the de-salinization plants and reservoirs, and \$92 billion dollars, for a total of \$171 billion dollars. However, given the massive cost to the economy of droughts such as the 2012-2013 drought, we contend that it will is the most cost-effective solution to the United States' water problems.

@@

We begin our paper with a projection of the likely levels of water
demand in the United States by 2025 on a county-by-county basis. Our primary source of data is the County-level water use data made publically available
by the US Geological Survey (USGS) in years 1985, 1990, 1995, 2000,
and 2005 \cite{key-2,key-3,key-4,key-5,key-6}. While making these projections, we assume that water use
equals the current water demands.

@@

This paper is  concerned with the construction of new water
supply infrastructure. Thus, there are some aspects of the water management
process that will not be further considered: 
\begin{itemize}
\item Public education: As with all issues of resource conservation, the
behaviour of the general public has an effect on water supplies. This
will not be considered here, for several reasons. The key issue is
that there is a lack of empirical evidence suggesting that currently
known public education strategies will work to minimise water usage
in the United States (developing such strategies further is beyond
the scope of this paper). The United States in particular has been
particularly resistant to attempts to reduce per capita water consumption\cite{key-7}.
More generally, even water education programmes considered particularly
successful, such as that of Singapore, have not managed to make a
huge impact on consumption, with an approximate 5 per cent reduction
in household water use over 6 years\cite{key-8}. Finally, the effect
of water education programmes is likely to have a similar effect in
each location. This means that areas that would be most in need of
additional infrastructure taking into account such programmes would
be essentially the same as those areas most in need while not taking
into account such programmes. 
\item Maintenance costs of current infrastructure: minimizing maintenance
costs depends on technological advancement and management, but is
essentially a fixed cost irrespective of the new infrastructure we
decide to implement.
\item Cost of obtaining data: Much of our analysis depends on USGS data.
We note that the cost of obtaining this survey data is negligible
(the WaterSMART initiative, which collects much of the data, cost
\$21 million this year\cite{key-9}. In comparison, de-salinization
facilities can easily cost billions to construct\cite{key-10}) compared
to the utility of superior decision making in constructing water-related
infrastructure (among various other things the data is useful for).
\end{itemize}

@@

Based on the above prediction, overall water demand in the United States will increase by 5.66 billion gallons per day between 2013 and 2025. 
Multiplying by the average cost of de-salinization facilities ($14  million per billion gallons per day) noted above, it would cost \$79.24 billion to build enough de-salinization plants to meet this demand.
